Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2020-12-08 xrb2/paper.tex
ack tweak
update table
update figure
more text

The initial model is setup in the same fashion as described in
\citet{flame_wave1}.  In particular, we create a ``hot'' and ``cool''
hydrostatic model representing the ash and fuel states and blend the
two models laterally to create a hot region near the origin of
coordinates and a smooth transition to the cooler region at larger
radii.  The cool initial characterized by 3 temperatures:
$T_\mathrm{star}$ is the isothermal temperature of the underlying
neutron star, $T_\mathrm{hi}$ is the temperature at the base of the
fuel layer, and $T_\mathrm{lo}$ is the minimum temperature of the
atmosphere---the atmosphere structure is isentropic as it falls from
$T_\mathrm{hi}$ down to $T_\mathrm{lo}$.  For the hot model, we
replace $T_\mathrm{hi}$ with $T_\mathrm{hi} + \delta T$.  In the
calculations presented here, we explore the structure of the initial
models by varying these parameters, in particular, the
temperature of the neutron star and at the base of the fuel layer.

@@

\begin{deluxetable}{lrrrrr}
	\tablecaption{\label{table:runs} Rotation rate and temperature properties of the simulations.}
	\tablehead{\colhead{run} & \colhead{Rotation Rate (Hz)} & \colhead{$\delta T$ (K)} & \colhead{$T_\mathrm{hi}$ (K)} & \colhead{$T_\mathrm{star}$ (K)}} 
	\startdata
	{\tt F1000}     & $1000$ & $1.2\times 10^9$ & $2\times 10^8$ & $10^8$ \\
	{\tt F500}      & $500$ & $1.2\times 10^9$ & $2\times 10^8$ & $10^8$ \\
	{\tt F500\_2E8} & $500$ & $1.2\times 10^9$ & $2\times 10^8$ & $2\times 10^8$ \\
	{\tt F500\_3E8} & $500$ & $1.1\times 10^9$ & $3\times 10^8$ & $3\times 10^8$ \\
	{\tt F500\_4E8} & $500$ & $10^9$ & $4\times 10^8$ & $4\times 10^8$ \\
	{\tt F250}      & $250$ & $1.2\times 10^9$ & $2\times 10^8$ & $10^8$ \\
	\enddata
\end{deluxetable}

@@

Things to show:

@@

\begin{figure}[t]
\centering
\plotone{compare_500Hz_abar}
\caption{\label{fig:compare_500Hz_abar} Comparison of $\bar{A}$ for 3 different 500~Hz models with different neutron star temperatures, $T_\star$, and resulting envelope structures. } %This will be updated to show at 70ms
\end{figure}

@@

\acknowledgments \castro\ is open-source and freely available at
\url{http://github.com/AMReX-Astro/Castro}.  The problem setups used
here are available in the git repo as {\tt flame} and {\tt
  flame\_wave}.  The work at Stony Brook was supported by DOE/Office
of Nuclear Physics grant DE-FG02-87ER40317.  This material is based upon work supported by the
U.S. Department of Energy, Office of Science, Office of Advanced
Scientific Computing Research and Office of Nuclear Physics, Scientific
Discovery through Advanced Computing (SciDAC) program under Award
Number DE-SC0017955.  This material is also based upon work supported by the U.S. Department
of Energy, Office of Science, Office of Advanced Scientific Computing Research, Department of
Energy Computational Science Graduate Fellowship under Award Number DE-SC0021110.
MZ acknowledges support from the Simons Foundation. 
This research used resources of the National Energy
Research Scientific Computing Center, a DOE Office of Science User
Facility supported by the Office of Science of the U.~S.\ Department
of Energy under Contract No.\ DE-AC02-05CH11231.  This research used
resources of the Oak Ridge Leadership Computing Facility at the Oak
Ridge National Laboratory, which is supported by the Office of Science
of the U.S. Department of Energy under Contract No. DE-AC05-00OR22725,
awarded through the DOE INCITE program.  We thank NVIDIA Corporation
for the donation of a Titan X and Titan V GPU through their academic
grant program.  This research has made use of NASA's Astrophysics Data
System Bibliographic Services.

>>>>

The initial model is setup in the same fashion as described in
\citet{flame_wave1}.  In particular, we create a ``hot'' and ``cool''
hydrostatic model representing the ash and fuel states and blend the
two models laterally to create a hot region near the origin of
coordinates and a smooth transition to the cooler region at larger
radii.  The cool initial characterized by 3 temperatures:
$T_\mathrm{star}$ is the isothermal temperature of the underlying
neutron star, $T_\mathrm{hi}$ is the temperature at the base of the
fuel layer, and $T_\mathrm{lo}$ is the minimum temperature of the
atmosphere---the atmosphere structure is isentropic as it falls from
$T_\mathrm{hi}$ down to $T_\mathrm{lo}$.  For the hot model, we
replace $T_\mathrm{hi}$ with $T_\mathrm{hi} + \delta T$.  In the
calculations presented here, we explore the structure of the initial
models by varying these parameters.  All models have the same
peak temperature in the hot model, $T_\mathrm{star} + \delta T$.

@@

\begin{deluxetable}{lrrrrr}
	\tablecaption{\label{table:runs} Rotation rate and temperature properties of the simulations.}
	\tablehead{\colhead{run} & \colhead{Rotation Rate (Hz)} & \colhead{$\delta T$ (K)} & \colhead{$T_\mathrm{hi}$ (K)} & \colhead{$T_\mathrm{star}$ (K)} & \colhead{$T_\mathrm{lo}$ (K)}} 
	\startdata
	{\tt F1000}     & $1000$ & $1.2\times 10^9$ & $2\times 10^8$ & $10^8$ & $8\times 10^6$ \\
	{\tt F500}      & $500$ & $1.2\times 10^9$ & $2\times 10^8$ & $10^8$ & $8\times 10^6$ \\
	{\tt F500\_2E8} & $500$ & $1.2\times 10^9$ & $2\times 10^8$ & $2\times 10^8$ & $8\times 10^6$ \\
	{\tt F500\_3E8} & $500$ & $1.1\times 10^9$ & $3\times 10^8$ & $3\times 10^8$ & $8\times 10^6$ \\
	{\tt F500\_4E8} & $500$ & $10^9$ & $4\times 10^8$ & $4\times 10^8$ & $8\times 10^6$ \\
	{\tt F250}      & $250$ & $1.2\times 10^9$ & $2\times 10^8$ & $10^8$ & $8\times 10^6$ \\
	\enddata
\end{deluxetable}

@@

We run 3 models (F250, F500, and F1000) with the same initial model but differing rotation rates.

@@

\begin{figure}[t]
\centering
\plotone{compare_500Hz_abar}
\caption{\label{fig:compare_500Hz_abar} Comparison of $\bar{A}$ for 3 different 500~Hz models with different neutron star temperatures, $T_\star$, and resulting envelope structures.  Each flame is shown at 70~ms.} %This will be updated to show at 70ms
\end{figure}

@@

\acknowledgments \castro\ is open-source and freely available at
\url{http://github.com/AMReX-Astro/Castro}.  The problem setup used
here is available in the git repo as {\tt
  flame\_wave}.  The work at Stony Brook was supported by DOE/Office
of Nuclear Physics grant DE-FG02-87ER40317.  This material is based upon work supported by the
U.S. Department of Energy, Office of Science, Office of Advanced
Scientific Computing Research and Office of Nuclear Physics, Scientific
Discovery through Advanced Computing (SciDAC) program under Award
Number DE-SC0017955.  This material is also based upon work supported by the U.S. Department
of Energy, Office of Science, Office of Advanced Scientific Computing Research, Department of
Energy Computational Science Graduate Fellowship under Award Number DE-SC0021110.
MZ acknowledges support from the Simons Foundation. 
This research used resources of the National Energy
Research Scientific Computing Center, a DOE Office of Science User
Facility supported by the Office of Science of the U.~S.\ Department
of Energy under Contract No.\ DE-AC02-05CH11231.  This research used
resources of the Oak Ridge Leadership Computing Facility at the Oak
Ridge National Laboratory, which is supported by the Office of Science
of the U.S. Department of Energy under Contract No. DE-AC05-00OR22725,
awarded through the DOE INCITE program.  We thank NVIDIA Corporation
for the donation of a Titan X and Titan V GPU through their academic
grant program.  This research has made use of NASA's Astrophysics Data
System Bibliographic Services.
